
\section{Related work}\label{sec:relatedwork}
Many methods for static memory-leak freedom verification have been
proposed~\cite{DBLP:conf/aplas/SuenagaK09,DBLP:conf/pldi/HeineL03,DBLP:conf/sigsoft/XieA05,DBLP:journals/scp/SwamyHMGJ06,DBLP:conf/sas/OrlovichR06,DBLP:conf/issta/SuiYX12}. These
methods guarantee partial memory-leak freedom and lack of illegal
accesses, whereas our type system guarantees total memory-leak
freedom. By using both their methods and our type system, we can
guarantee safe memory deallocation for nonterminating programs.

Behavioral types are extensively studied in the context of concurrent
program
verification~\cite{DBLP:conf/esop/HondaVK98,DBLP:journals/tcs/IgarashiK04,DBLP:conf/esop/VieiraCS08,DBLP:journals/lmcs/KobayashiSW06}.
These type systems guarantee that the communication pattern of
concurrent programs are as intended.  Our type system is largely
inspired by one by Kobayashi et
al.~\cite{DBLP:journals/lmcs/KobayashiSW06}, which guarantees that a
concurrent program accesses resources according to specification.

Model checking~\cite{clarke1999model,ben2008principles,beyer2011cpachecker} is a widely used technique for automatically
verifying correctness properties of finite-state system. We assume
that some model checkers solves the constraints \(\OK_\nu(P)\) in our
paper. We expect that applying model checker to inferred behavioral
types is better than to the original programs, because a behavioral
type focuses on the actions related to allocations and deallocations,
abstracted away from other features. We plan to do some experiments
for this prospects.


